### 2017-05-01 R/ITHIM.Rmd
Restructuring GBD by State data
Debugging ITHIM.Rmd

gbdParse <- function(gbd){
  gbdListTemp <- split(gbd,gbd$disease)
  gbdListTemp[["CVD"]] <- data.frame(disease = "CVD", gbdListTemp$IHD[,c("sex",  "ageClass")], gbdListTemp$IHD[,c("dproj","yll","yld","daly")] + gbdListTemp$InflammatoryHD[,c("dproj","yll","yld","daly")] + gbdListTemp$HHD[,c("dproj","yll","yld","daly")])
  gbdListTemp2 <- lapply(gbdListTemp,function(x) split(x,as.factor(x$sex)))
  gbdListTemp2 <- lapply(gbdListTemp2, function(x) list(M=x$M,F=x$F))
  return(gbdListTemp2)
}

@@

gbdByState <- split(gbdRDS,gbdRDS$state)
gbdByState <- lapply(gbdByState, function(x) x[,!names(x)=="state"])
gbdList <- lapply(gbdByState, gbdParse)

@@

ITHIM.default <- update(ITHIM.default, list( cvNonTravel = 3, cv = 1.65, muNonTravel = 4, muNonTravelMatrix = METmatrix, quantiles = (1:9)/10 ) )

@@

@@

getDALY <- function( ITHIM ){
foo <- data.frame(lapply(ITHIM@parameters@GBD, function(x) x$M$daly + x$F$daly))
sum(foo[,names(foo) %in% c("BreastCancer","ColonCancer","Dementia","Depression","Diabetes", "CVD")])
}

burdenList <- lapply(ITHIMList, getDALY)
foo <- data.frame(daly = unlist(burdenList), delta = deltaDALYList)
foo <- within(foo, {
  daly <- daly + delta
  delta <- -delta
  state <- names(burdenList)
})

foo <- subset(foo, state %in% c("MI","OH"))

D <- melt(foo)

@@

p <- ggplot(D, aes(state, value/1e3, fill = variable))
p + geom_bar(stat= "identity") + scale_x_discrete(name="") + scale_y_continuous(name="Thousands of DALYs") + guides(fill=FALSE) + scale_fill_manual(values=cbPalette) + theme(axis.text.y  = element_text(size = 16)) + theme(axis.text.x  = element_text(size = 16), axis.title.x  = element_text(size = 16)) + coord_flip()
```

>>>>

gbdParse <- function(gbd){
  gbdListTemp <- split(gbd,gbd$disease)
  gbdListTemp2 <- lapply(gbdListTemp,function(x) split(x,as.factor(x$sex)))
  gbdListTemp2 <- lapply(gbdListTemp2, function(x) list(M=x$M,F=x$F))
  return(gbdListTemp2)
}

@@

GBD <- bind_rows(
  gbdRDS %>%
  melt() %>%
  filter(disease %in% c("IHD", "HHD", "InflammatoryHD")) %>%
  group_by(state, sex, ageClass, variable) %>% summarise(value = sum(value)) %>%
  mutate(disease = "CVD"),
  gbdRDS %>%
  melt() %>%
  filter(disease %in% c("BreastCancer","ColonCancer","Dementia", "Diabetes", "Depression", "RTIs"))
)

GBD <- within(GBD, {
  variable <- ifelse(variable == "dproj","deaths", as.character(variable))
})

GBD <- with(GBD, data.frame(state, disease, sex, ageClass, variable, value, stringsAsFactors = FALSE)) %>% arrange(state,disease,sex,ageClass,variable)

gbdByState <- split(GBD,GBD$state)
gbdByState <- lapply(gbdByState, function(x) x[,!names(x)=="state"])
gbdList <- lapply(gbdByState, gbdParse)

@@

ITHIM.default <- update(ITHIM.default, list( cvNonTravel = 3, cv = 1.65, muNonTravel = 4, muNonTravelMatrix = METmatrix, quantiles = (1:99)/100 ) )

@@

ITHIMList <- ITHIMList[names(ITHIMList) != "Natl."] # The national ITHIM obnject needs to have GBD updated.

@@

## getDALY <- function( ITHIM ){
## foo <- data.frame(lapply(ITHIM@parameters@GBD, function(x) x$M$daly + x$F$daly))
## sum(foo[,names(foo) %in% c("BreastCancer","ColonCancer","Dementia","Depression","Diabetes", "CVD")])
## }

## burdenList <- lapply(ITHIMList, getDALY)
## foo <- data.frame(daly = unlist(burdenList), delta = deltaDALYList)
## foo <- within(foo, {
##   daly <- daly + delta
##   delta <- -delta
##   state <- names(burdenList)
## })

## foo <- subset(foo, state %in% c("MI","OH"))

## D <- melt(foo)

@@

## p <- ggplot(D, aes(state, value/1e3, fill = variable))
## p + geom_bar(stat= "identity") + scale_x_discrete(name="") + scale_y_continuous(name="Thousands of DALYs") + guides(fill=FALSE) + scale_fill_manual(values=cbPalette) + theme(axis.text.y  = element_text(size = 16)) + theme(axis.text.x  = element_text(size = 16), axis.title.x  = element_text(size = 16)) + coord_flip()
```
